%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Engineering Manager} % Job title
    {Netflix} % Organisation
    {Los Angeles, CA} % Location
    {Mar 2021 - Apr 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of 10 full stack and data engineers supporting the Netflix Studio.}
        \item {Grew engineering team from 6 to 10 engineers.}
        \item {Developed job family description and leveling criteria for bespoke engineering team.}
        \item {Collaborated with stakeholders and product managers to enhance our engagement model with the Studio users.}
        \item {Led cross functional team in charge of identifying use cases for 3rd party application audit logs.}
      \end{cvitems}
    }
  
  \cventry
    {Sr. Director of Engineering} % Job title
    {NBC Universal} % Organisation
    {Universal City, CA} % Location
    {Aug 2019 - Mar 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed multiple client engineering teams for NBC's streaming platform, including the iOS, Android, Connected TV, Web, and Identity teams.}
        \item {Shaped the short-term and long-term technical direction for the client platform teams.}
        \item {Guided technical integration of 3rd party video player into multiple client platforms to provide a consistent UX to users.}
        \item {Coordinated release management across multiple platform teams.}
      \end{cvitems}
    }
    
  \cventry
    {Tech Lead} % Job title
    {Gorilla Logic - NBC Universal Contract} % Organisation
    {Universal City, CA} % Location
    {Aug 2016 - Aug 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a distributed team of 8 full stack engineers that consisted of a mix of full time and contract engineers spanning multiple timezones.}
        \item {Collaborated with product and design partners to craft first-class streaming experience.}
        \item {Identified inefficiencies with our QA process and implemented process improvements to facilitate faster release cycles.}
      \end{cvitems}
    }

  \cventry
    {Sr. Software Engineer} % Job title
    {Verizon Digital Media Services} % Organisation
    {Playa Vista, CA} % Location
    {Aug 2014 - Aug 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Aided in migration of digital ad insertion platform after sale from Disney to Verizon.}
        \item {Improved overall efficiency and maintainability of key software components by migrating from PHP to nodeJS.}
        \item {Coordinated release efforts.}
      \end{cvitems}
    }


  \cventry
    {Sr. Software Engineer} % Job title
    {Disney ABC} % Organisation
    {Burbank, CA} % Location
    {Aug 2012 - Aug 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated as key member of a large, fast-paced, cross-functional team building a first-of-its-kind dynamic ad insertion platform.}
        \item {Spearheaded development of middle-tier integration system responsible for reacting to broadcast events.}
        \item {Collaborated cross-functionally with broadcast engineers and platform engineers to deploy software to multiple local broadcast stations.}
      \end{cvitems}
    }

  \cventry
    {Manager, Technology} % Job title
    {Sapient Nitro - Disney Interactive Group Contract} % Organisation
    {North Hollywood, CA} % Location
    {May 2012 - Aug 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in migration of content from proprietary CMS to Drupal.}
        \item {Design and develop custom CMS modules for feature parity from existing CMS.}
        \item {Led efforts to Integrate Apache SOLR search to the product.}
      \end{cvitems}
    }

  \cventry
    {Software Developer} % Job title
    {Causecast} % Organisation
    {Culver City, CA} % Location
    {May 2010 - May 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in development of donation and volunteering platform through coding, testing and documenting in an agile environment.}
        \item {Responsible for operational reporting needs for key decision makers including CEO.}
        \item {Provided leadership and direction for junior level developers.}
      \end{cvitems}
    }
\end{cventries}
